---
title: "Untitled"
author: "Paul Oldham"
date: "21/05/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Rough initial workings on sentiment analysis for AI tweets. Uses the Silge and Robinson *Text Mining with R: A Tidy Approach* from which the code is adapted. 

Takes the 9175 AI seed tweets.

```{r}
library(tidytext)
# divide into words and remove stopwords
ai_tokens <- AI %>%
  unnest_tokens(., word, text) %>% 
  anti_join(stop_words)

# count up and rank the words
ai_tokens %>% 
  count(word, sort = TRUE)
```

```{r}
# join to sentiments dictionary (in this case bing)
ai_sentiment <- ai_tokens %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment) %>%
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive - negative)
ai_sentiment
```

```{r}
# What are the top positive terms in the tweets

ai_sentiment %>% 
  arrange(desc(sentiment))
```


```{r}
# Wnat are the top ranking negative terms
ai_sentiment %>% 
  dplyr::filter(sentiment <= 0) %>%
  arrange(sentiment)
```





# This is a very raw quick look at sentiments to see what comes up
# No banana yet
ai_sentiment %>% 
  count(word, sentiment, sort = TRUE) %>% ungroup() %>% 
  group_by(sentiment) %>%
  dplyr::top_n(5) %>%
  ungroup() %>% 
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n, fill = sentiment)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~sentiment, scales = "free_y") +
  labs(y = "Contribution to sentiment",
       x = NULL) +
  coord_flip()



```